The ChEMBL database as Linked Open Data

### 2012-02-27 article.tex
Some text to give some idea where this is going

\begin{abstract}
An abstract,
\end{abstract}

\begin{keyword}
 \sep Resource Description Framework
\end{keyword}

@@

%\section{}\label{s1}

@@

@@

>>>>

\begin{abstract}
This paper describes the continued conversion of ChEMBL data into RDF triples, using a few existing
ontologis, and demonstrates a few new use cases, taking advantage of its linked nature.
\end{abstract}

\begin{keyword}
% \sep 
Resource Description Framework, ChEMBL
\end{keyword}

@@

\section{Introduction}\label{s1}

Linked Data, pharmaceutical research, Open PHACTS, ...

This data set has been previously used in~\cite{} and \cite{} and some used practices have
been described in \cite{}...

@@

\section{Methods}\label{s2}

The ChEMBL version used in this paper is ChEMBL 12, which was released on ....

\subsection{Ontologies}

Ontologies... CHEMINF, ...

The BIBO ontology is used to represent documents.

\subsection{Use cases}

John/Anna: common statistics with SPARQL

Ola: use in BC-DS for possible adverse reactions

Andra: CitedIn

The link between data and formal publication is important in many areas of
attribution, scientist ranking, etc, as outline in \cite{Waagmeester2012}.
ChEMBL contains many literature references, and we wish to query this data
for CitedIn.

Peter: Bio2RDF

David: Chem2Bio2RDF

\section{Results}\label{s3}

Previously, a SPARQL end point has been set up at Uppsala University.

Later, to satisfy the requirements for the Linked Open Drug Data \cite{}
network, the data was also hosted on Kasabi, a triple store hosting service
free for Open Data~\cite{}.

\# triples
\# links out
\# problems

For each of the common resource classes a triple pattern was defined, following the
data available in the relational database.

Assays .... anything

\begin{verbatim}
\end{verbatim}

Targets ... protein, other

\begin{verbatim}
\end{verbatim}

Activities ...

\begin{verbatim}
\end{verbatim}

Compounds ... Three types of compounds, peptides, small chemicals, ...

\begin{tiny}
\begin{verbatim}
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2000/01/rdf-schema#label> "Bis(3-[14-Benzyl-11-(1H-indol-3-ylmethyl)-2-isobutyl-13-methyl-5-(2-methylsulfanyl-ethyl)-3,6,9,12,15,20-hexaoxo-1,4,7,10,13,16-hexaaza-bicyclo[15.2.1]icos-18-en-8-yl]-propionamide)" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2000/01/rdf-schema#subClassOf> <http://semanticscience.org/resource/CHEMINF_000000> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2002/07/owl#equivalentClass> <http://bio2rdf.org/chebi:100041> .
<http://data.kasabi.com/dataset/chembl-rdf/chemblid/CHEMBL406142> <http://www.w3.org/2002/07/owl#equivalentClass> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2002/07/owl#equivalentClass> <http://data.kasabi.com/dataset/chembl-rdf/chemblid/CHEMBL406142> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2000/01/rdf-schema#label> "CHEMBL406142" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.blueobelisk.org/chemistryblogs/smiles> "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://semanticscience.org/resource/CHEMINF_000200> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/smiles> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/smiles> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://semanticscience.org/resource/CHEMINF_000018> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/smiles> <http://semanticscience.org/resource/SIO_000300> "CC(C)C[C@@H]1N2C=CC(NC(=O)[C@H](Cc3ccccc3)N(C)C(=O)C(Cc4c[nH]c5ccccc45)NC(=O)C(CCC(=O)N)NC(=O)[C@@H](CCSCCSCC[C@H]6NC(=O)[C@H](CC(C)C)N7C=CC(NC(=O)[C@H](Cc8ccccc8)N(C)C(=O)C(Cc9c[nH]c%10ccccc9%10)NC(=O)C(CCC(=O)N)NC6=O)C7=O)NC1=O)C2=O" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.blueobelisk.org/chemistryblogs/inchi> "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://semanticscience.org/resource/CHEMINF_000200> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchi> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchi> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://semanticscience.org/resource/CHEMINF_000113> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchi> <http://semanticscience.org/resource/SIO_000300> "InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.w3.org/2002/07/owl#equivalentClass> <http://rdf.openmolecules.net/?InChI=1S/C82H102N16O14S2/c1-47(2)39-67-77(107)89-59(73(103)87-57(25-27-69(83)99)71(101)93-63(43-51-45-85-55-23-15-13-21-53(51)55)79(109)95(5)65(41-49-17-9-7-10-18-49)75(105)91-61-29-33-97(67)81(61)111)31-35-113-37-38-114-36-32-60-74(104)88-58(26-28-70(84)100)72(102)94-64(44-52-46-86-56-24-16-14-22-54(52)56)80(110)96(6)66(42-50-19-11-8-12-20-50)76(106)92-62-30-34-98(82(62)112)68(40-48(3)4)78(108)90-60/h7-24,29-30,33-34,45-48,57-68,85-86H,25-28,31-32,35-44H2,1-6H3,(H2,83,99)(H2,84,100)(H,87,103)(H,88,104)(H,89,107)(H,90,108)(H,91,105)(H,92,106)(H,93,101)(H,94,102)/t57?,58?,59-,60-,61?,62?,63?,64?,65+,66+,67+,68+/m1/s1> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://www.blueobelisk.org/chemistryblogs/inchikey> "LMCOMIDLRGMFCZ-RIPOXUOASA-N" .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41> <http://semanticscience.org/resource/CHEMINF_000200> <http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchikey> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchikey> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://semanticscience.org/resource/CHEMINF_000059> .
<http://data.kasabi.com/dataset/chembl-rdf/molecule/m41/inchikey> <http://semanticscience.org/resource/SIO_000300> "LMCOMIDLRGMFCZ-RIPOXUOASA-N" .
\end{verbatim}
\end{tiny}

For documents little information is replicated from the database, taking advantage
of PubMed Identifiers (PMIDs) and Digital Object Identifiers (DOIs). URIs for the
latter can be resolved online, providing curated information on the identified
documents. For PubMed articles ...

\begin{tiny}
\begin{verbatim}
<http://data.kasabi.com/dataset/chembl-rdf/journal/j6c706049c2e08871b7c46a6528065736> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://purl.org/ontology/bibo/Journal> .
<http://data.kasabi.com/dataset/chembl-rdf/journal/j6c706049c2e08871b7c46a6528065736> <http://purl.org/dc/elements/1.1/title> "J. Med. Chem." .

<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://purl.org/ontology/bibo/Article> .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/pmid> "14695813" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://www.w3.org/2000/01/rdf-schema#seeAlso> <http://bio2rdf.org/pubmed:14695813> .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/dc/elements/1.1/date> "2004" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/volume> "47" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/issue> "1" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/pageStart> "1" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/ontology/bibo/pageEnd> "9" .
<http://data.kasabi.com/dataset/chembl-rdf/resource/r1> <http://purl.org/dc/elements/1.1/isPartOf> <http://data.kasabi.com/dataset/chembl-rdf/journal/j6c706049c2e08871b7c46a6528065736> .
\end{verbatim}
\end{tiny}

\# results of use cases

\section{Discussion}

outlook ...

\section{Acknowledgements}

Kasabi.

@@

\printbibliography
